Aspects of RDF Data Constraints in the Social, Behavioural, and Economic Sciences

### 2015-07-14 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
evaluation

\begin{abstract}
%\boldmath
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
In this paper, we formulate 213 constraints of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classify them according to the complexity level of their type and their severity level. For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
Based on the results, we formulate several hypotheses to direct the further development of constraint languages.\textcolor{red}{81 constraint types instead of 82?}
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

The social, behavioural, and economic sciences (\emph{SBE}) require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
an XML format to disseminate, manage,
and reuse data collected and archived for research \cite{Vardigan2008}. 
%DDI is heavily used by the CESSDA community of European national data archives, 
%the International Household Survey Network community (made up of more than 90 statistical agencies),
%and ICPSR - the largest SBE data archive in the US.
In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration. Therefore, not only established vocabularies like \emph{SKOS} are used; 
recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.

For constraint formulation and validation of RDF data, several languages exist or are currently developed, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}. \emph{OWL 2} is also used as a constraint language under a closed world assumption. With its direct support of validation via SPARQL, \emph{SPIN}%\footnote{\url{http://spinRDF.org/}}
is very popular and certainly plays an important role for future developments in this field. It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}. Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners. Further research and development therefore is needed.

@@

As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
For 114 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
Based on the evaluation results,
we formulated several hypotheses to direct the further development of constraint languages.
To make valid general statements for all vocabularies, however,
the hypotheses still have to be verified or falsified
by evaluating the quality of data represented by more than three vocabularies (Section \ref{evaluation}).
%The \textbf{contribution} of this paper is the development of a system 
%\begin{enumerate}
	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%\end{enumerate}
%By defining a huge amount of constraints of the majority of the constraint types,   
%we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
%A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
%We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
%how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
%how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding 
%(1) which sets of constraint types (on different levels of complexity) and 
%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

@@

By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
%In performing their research, the detailed person-level
%data is aggregated into multi-dimensional tables which answer particular research questions.
Aggregated data, which answers particular research questions, is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
%The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
%Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
%allowing the RDF versions of these standards to retain that alignment.
%While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
%both on a different level of aggregation, 
%the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives. 
%The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
%Although, in most cases aggregated data is still published in form of PDFs, 
%it is more and more common to publish aggregated data as CSV files,
The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
Aggregated data is published in form of CSV files,
allowing to perform calculations on the data.
%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
%\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF.\tb{tabular data} 
%The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
%Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
%\tb{To ensure high quality, data must satisfy certain criteria - specified in terms of RDF constraints.}

@@

%\textbf{RDF Data Cube Vocabulary.}
A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the \emph{QB} specification, passes.
Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more \emph{QB} instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
Mader, Haslhofer, and Isaac investigated how to support
taxonomists in improving SKOS vocabularies by pointing out quality
issues that go beyond the integrity constraints defined in the SKOS specification \cite{MaderHaslhoferIsaac2012}.

@@

%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.

@@

%\textbf{Metadata on Aggregated Data.}
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e. multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}. 
%\emph{QB} represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
The variable \emph{formal childcare}, e.g., is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}. 
%(e.g., the year in which \emph{formal childcare} has been determined).
%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen? Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}

@@

It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and build URIs from user inputs and imported data. 
In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
which is therefore inverse-functional $({\small\ms{funct identifier}\sp{\overline{\ }}})$,
i.e., for each \emph{rdfs:Resource x}, there can be at most one distinct resource \emph{y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} (\emph{error}).
%\begin{DL}
%$(\ms{funct identifier}\sp{\overline{\ }})$
%\end{DL} 
Keys, however, are even more general than \emph{inverse-functional properties} (\emph{R-58}),
as a key can be a data property, an object property, or a chain of properties \cite{Schneider2009}.
Thus and as there are different sorts of key, and as keys can lead to undecidability, 
DL is extended with the construct \emph{keyfor} ({\small\ms{identifier \ms{keyfor} Resource}}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
%\emph{OWL 2} \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
%\begin{DL}
%identifier \ms{keyfor} Resource
%\end{DL}

@@

%For assessing the quality of \emph{SKOS} vocabularies, we concentrate on graph-based structures and apply graph- and network-analysis techniques (\emph{structure} constraints) like 

@@

%In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},

@@

%Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).

@@

In this section, we describe our findings based on an automatic constraint checking of a large data set. Despite the large volume of the data set in general, we have to keep in mind that this study only uses data for three vocabularies. As described in Section~\ref{rdf-representation}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions. The three vocabularies, however, are representative, cover different aspects of SBE data and are also a mixture of established vocabularies (\emph{QB}, \emph{SKOS}) and a vocabulary under development (\emph{Disco}). Due to this limitation, we will present several hypotheses together with a rationale based on the results for the three vocabularies. If the hypotheses hold generally is still to be determined, nevertheless they should provide valuable insights for future developments of constraint languages.

@@

	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$). 
On the three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}), we identified and classified 213 constraints of which we implemented for the data validation 114 constraints.\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} The reason is simply that more time is needed for the remaining implementation. We ensured, however, that the implementation is equally distributed over the classes and vocabularies we have. We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these 114 constraints, obtained from 33 SPARQL endpoints.

\emph{QB} and \emph{SKOS} are well-established vocabularies which are widely adopted and accepted. \emph{Disco} is a newly developed vocabulary which will be published in 2015.

@@

Table~\ref{tab:datasets} lists the number of data sets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics},
the \emph{European Central Bank}, and the
\emph{Organisation for Economic Co-operation and Development},
(2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
the \emph{STW Thesaurus for Economics}, and the
\emph{Thesaurus for the Social Sciences}, and
(3) \emph{Disco} data sets provided by the \emph{Microdata Information System}, 
the \emph{Data Without Boundaries Discovery Portal}, the
\emph{Danish Data Archive}, and the
\emph{Swedish National Data Service}.

@@

    \\ \midrule
		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
		%\hline
		\textbf{\emph{QB}} & $9,990$   & $3,775,983,610$  \\
		\textbf{\emph{SKOS}} & $4,178$  & $477,737,281$ \\
		\textbf{\emph{Disco}} & $1,526$  & $9,673,055$  \\
    \bottomrule
    \end{tabular}
    %\\ \emph{C (constraints), CT (constraint types)}
    \end{center}
\end{table}

@@

We use \emph{SPIN}, 
a SPARQL-based way to formulate and check constraints, as basis to develop a
validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.

@@

%Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
The \emph{SPIN} engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
There is one \emph{SPIN} construct template for each constraint type.
A \emph{SPIN} construct template contains a \emph{SPARQL CONSTRUCT} query which generates constraint violation triples indicating the subject and the properties causing constraint violations, and the reason why constraint violations have been raised.
A \emph{SPIN} construct template creates constraint violation triples if all triple patterns within the \emph{SPARQL WHERE clause} match.
%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in form of multiple concrete syntaxes.

@@

80\% of the \emph{QB} constraints are \emph{error constraints}.
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are \emph{informational constraints}.
1/6 of the Disco violations are caused by \emph{error constraints} and
almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by \emph{warning constraints}.  
For well-established vocabularies, data quality is high
as serious violations rarely appear.
For newly developed vocabularies, data quality is worse
as serious violations occur partially.
%Constraints are serious when they violate the integrity of vocabularies.
%For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity
%which is not the case or newly-developed vocabularies.
\begin{hyp}
Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet reduce severe violations.   
\end{hyp}

%For the vocabularies \emph{Disco}, \emph{QB}, and \emph{SKOS}, we defined 213 constraints of 53 constraint types .

>>>>

\begin{abstract}
%\boldmath
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
In this paper, we formulate 213 constraints of 53 different types on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to the complexity level of their type and their severity level. For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
Based on the results, we formulate several hypotheses to direct the further development of constraint languages.\textcolor{red}{81 constraint types instead of 82?}
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\textcolor{red}{references to constraint languages}

The social, behavioural, and economic sciences (\emph{SBE}) require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
an XML format to disseminate, manage,
and reuse data collected and archived for research \cite{Vardigan2008}. 
%DDI is heavily used by the CESSDA community of European national data archives, 
%the International Household Survey Network community (made up of more than 90 statistical agencies),
%and ICPSR - the largest SBE data archive in the US.
In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration. Therefore, not only established vocabularies like SKOS are used; 
recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.

For constraint formulation and validation of RDF data, several languages exist or are currently developed, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}. \emph{OWL 2} is also used as a constraint language under a closed world assumption. With its direct support of validation via SPARQL, SPIN%\footnote{\url{http://spinRDF.org/}}
is very popular and certainly plays an important role for future developments in this field. It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}. Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners. Further research and development therefore is needed.

@@

As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
For 114 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
Based on the evaluation results,
we formulated several hypotheses to direct the further development of constraint languages.
To make valid general statements for all vocabularies, however,
the hypotheses still have to be verified or falsified
by evaluating the quality of data represented by more than three vocabularies (Section \ref{evaluation}).
%The \textbf{contribution} of this paper is the development of a system 
%\begin{enumerate}
	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%\end{enumerate}
%By defining a huge amount of constraints of the majority of the constraint types,   
%we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
%A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
%We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
%how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
%how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding 
%(1) which sets of constraint types (on different levels of complexity) and 
%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

@@

By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
%In performing their research, the detailed person-level
%data is aggregated into multi-dimensional tables which answer particular research questions.
Aggregated data, which answers particular research questions, is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
%The SDMX metadata standard – used as the basis for QB – and DDI have traditionally made efforts to align their content. 
%Similarly, some of the developers of DDI-RDF were also involved in the development of QB, 
%allowing the RDF versions of these standards to retain that alignment.
%While DDI-RDF and QB provide terms for the description of data sets, 
%both on a different level of aggregation, 
%the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives. 
%The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
%Although, in most cases aggregated data is still published in form of PDFs, 
%it is more and more common to publish aggregated data as CSV files,
The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
Aggregated data is published in form of CSV files,
allowing to perform calculations on the data.
%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
%\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF.\tb{tabular data} 
%The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
%Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
%\tb{To ensure high quality, data must satisfy certain criteria - specified in terms of RDF constraints.}

@@

%\textbf{RDF Data Cube Vocabulary.}
A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the QB specification, passes.
Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more QB instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
Mader, Haslhofer, and Isaac investigated how to support
taxonomists in improving SKOS vocabularies by pointing out quality
issues that go beyond the integrity constraints defined in the SKOS specification \cite{MaderHaslhoferIsaac2012}.

@@

%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (DDI-RDF), aggregated data sets (QB), thesauri (SKOS), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.

@@

%\textbf{Metadata on Aggregated Data.}
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e. multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}. 
%QB represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
The variable \emph{formal childcare}, e.g., is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}. 
%(e.g., the year in which \emph{formal childcare} has been determined).
%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen? Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}

@@

It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and build URIs from user inputs and imported data. 
In DDI-RDF, resources are uniquely identified by the property \emph{adms:identifier},
which is therefore inverse-functional $({\small\ms{funct identifier}\sp{\overline{\ }}})$,
i.e., for each \emph{rdfs:Resource x}, there can be at most one distinct resource \emph{y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} (\emph{error}).
%\begin{DL}
%$(\ms{funct identifier}\sp{\overline{\ }})$
%\end{DL} 
Keys, however, are even more general than \emph{inverse-functional properties} (\emph{R-58}),
as a key can be a data property, an object property, or a chain of properties \cite{Schneider2009}.
Thus and as there are different sorts of key, and as keys can lead to undecidability, 
DL is extended with the construct \emph{keyfor} ({\small\ms{identifier \ms{keyfor} Resource}}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
%\emph{OWL 2} \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
%\begin{DL}
%identifier \ms{keyfor} Resource
%\end{DL}

@@

%For assessing the quality of SKOS vocabularies, we concentrate on graph-based structures and apply graph- and network-analysis techniques (\emph{structure} constraints) like 

@@

%In DDI-RDF, resources are uniquely identified by the property \emph{adms:identifier},

@@

%Within the context of DDI-RDF, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).

@@

In this section, we describe our findings based on an automatic constraint checking of a large data set. Despite the large volume of the data set in general, we have to keep in mind that this study only uses data for three vocabularies. As described in Section~\ref{rdf-representation}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions. The three vocabularies, however, are representative, cover different aspects of \emph{SBE} data and are also a mixture of established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF). Due to this limitation, we will present several hypotheses together with a rationale based on the results for the three vocabularies. If the hypotheses hold generally is still to be determined, nevertheless they should provide valuable insights for future developments of constraint languages.

@@

	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$). 
On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 114 constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for the data validation. We ensured that the implementation of the constraints is equally distributed over the classes and vocabularies we have. We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these 114 constraints, obtained from 33 SPARQL endpoints.

QB and SKOS are well-established vocabularies which are widely adopted and accepted. DDI-RDF is a newly developed vocabulary which will be published in 2015.

@@

Table~\ref{tab:datasets} lists the number of data sets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
(1) QB data sets published by the \emph{Australian Bureau of Statistics},
the \emph{European Central Bank}, and the
\emph{Organisation for Economic Co-operation and Development},
(2) SKOS thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
the \emph{STW Thesaurus for Economics}, and the
\emph{Thesaurus for the Social Sciences}, and
(3) DDI-RDF data sets provided by the \emph{Microdata Information System}, 
the \emph{Data Without Boundaries Discovery Portal}, the
\emph{Danish Data Archive}, and the
\emph{Swedish National Data Service}.

@@

    \\ \midrule
		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
		%\hline
		\textbf{QB} & $9,990$   & $3,775,983,610$  \\
		\textbf{SKOS} & $4,178$  & $477,737,281$ \\
		\textbf{DDI-RDF} & $1,526$  & $9,673,055$  \\
    \bottomrule
    \end{tabular}
    %\\ \emph{C (constraints), CT (constraint types)}
    \end{center}
\end{table}

@@

We use \emph{SPIN}, a SPARQL-based way to formulate and check constraints, as basis to develop a
validation environment\footnote{Online demo available at: \url{http://purl.org/net/rdfval-demo}, source code at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.

@@

%Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
There is one SPIN construct template for each constraint type.
A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject and the properties causing constraint violations and the reason why constraint violations have been raised.
A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the DDI-RDF vocabulary in form of multiple concrete syntaxes.

@@

80\% of the QB constraints are \emph{error} constraints.
More than 50\% of the DDI-RDF and SKOS constraints, however, are \emph{informational} constraints.
1/6 of the Disco violations are caused by \emph{error} constraints and
almost all QB violations and 59\% of the SKOS violations are caused by \emph{warning} constraints.  
For well-established vocabularies, data quality is high
as serious violations rarely appear.
For newly developed vocabularies, data quality is worse
as serious violations occur partially.
%Constraints are serious when they violate the integrity of vocabularies.
%For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity
%which is not the case or newly-developed vocabularies.
\begin{hyp}
Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet reduce severe violations.   
\end{hyp}

%For the vocabularies DDI-RDF, QB, and SKOS, we defined 213 constraints of 53 constraint types .
